### 2014-08-29 paper/paper.Rmd
*very* rough treatment of shiny app

The PISA dataset contains dozens of household factors; we wanted a way to make our data-exploration more efficient. Moreover, we wanted a way that we could make explorations independent of each other, as during the course of the invesigation our team was in three cities over two hemispheres.

To make our exploration easier, we developed a "Shiny" app.

@@

>>>>

The PISA dataset contains hundreds of factors; we wanted a way to make our data-exploration more efficient.

Moreover, for much of the time when the authors made their initial investigations, we (they?) were remote from each other: four team-members, in three cities across, two hemispheres. Thanks to a ten-hour dime difference, we would meet, virtually, only occasionally, and we had to make the most of our limited time.

To make our exploration easier, we developed a "Shiny" app, so that we could show each other our ideas interactively.

"Let's look at *this* factor, combined with *that* factor!"

"Let's look at that other factor, instead."

@@

We then decided to look at only household factors. Inner factor, using boxplots. Outer factor, using violin plots. Added correlation by country.
